% Data Mining

In order to evaluate the performance of multiple stocks over given time periods, we needed to obtain a lengthy series of data.  We were able to obtain raw comma-separated value (csv) documents that detailed the end of day trading prices of all stocks listed on a given day for the New York Stock Exchange (NYSE).  The online vendor had to process these files and we waited about a day for them, but this was just the start\cite{back9}.  After receiving the csv data files we quickly moved to optimize portfolios over time horizons of greater than 20 days.  Within 20 days many stocks are added and removed from the exchange.  Ordering a matrix of prices for all of our stocks over the extended period of about 5 years in data we had purchased quickly became a daunting task.  We created an algorithm to handle the parsing of daily csv trading data that would be compiled in a centralized matrix of all stocks ever traded in the 5 year period.  More information on how we built our compiler can be found in the Appendix Section 1, and the exact MATLAB script can be found in Appendix Section 3.  

	We value the steps taken to organize the considerable time series of data.  When this optimization is executed over an extended and rolling time frame, having the 5 year data set will be tremendously important in testing of our optimal portfolio techniques.  Having an extended matrix of prices, also enabled us to observe multiple periods in the economy discretely.  We could choose to observe our optimization routine, on any month of daily price close data from January 2008 through October 2013.   That set of data is being kept and can be produced at request.